Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-24 paper.qmd
Updated Figure 16 b) with more useful projection

## First projection
projection <- cbind(
    c(0.71503,0.00502,-0.04370,-0.01811,-0.01103,0.09877,0.06199,0.05396,0.07771,-0.01713),
    c(0.00587,0.71879,0.03485,0.08284,-0.07534,-0.05420,0.04315,-0.00547,-0.02995,0.01810))

projection_scaled <- projection * 1.3

@@

@@

mnist_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    #size = 0.2,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000","#e41a1c")) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  #coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("b") +
  theme(
    legend.position = "none"
  )

>>>>

## First projection
# projection <- cbind(
#     c(0.71503,0.00502,-0.04370,-0.01811,-0.01103,0.09877,0.06199,0.05396,0.07771,-0.01713),
#     c(0.00587,0.71879,0.03485,0.08284,-0.07534,-0.05420,0.04315,-0.00547,-0.02995,0.01810))

projection <- cbind(
    c(-0.09936,0.36550,0.07658,0.29975,0.09085,-0.14009,-0.13417,0.48357,-0.00699,-0.13587),
    c(0.23061,0.19332,-0.11264,0.14797,0.30351,0.14980,0.02785,-0.30209,-0.13540,-0.43284))

projection_scaled <- projection * 2.5

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.83,
  axis_pos_y = -0.83,
  axis_labels = names(scaled_mnist_data),
  threshold = 0.06)

@@

mnist_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2,
      colour = cluster)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    #size = 0.2,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000","#e41a1c")) +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  #coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("b") +
  theme(
    legend.position = "none"
  )
